---
title: "assignment1"
author: "Sille Hasselbalch Markussen"
date: "2/8/2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
pacman::p_load(tidyverse)
```

## Defining general conditions
```{r}
set.seed(25)
trials <- 120
agents <- 100
```

## Implementing a random agent 
```{r}
RandomAgent <- function(input, rate){
  n <- length(input)
  choice <- rbinom(n, 1, rate)
  return(choice)
}

```


## Implementing win-shift-lose-stay agent

```{r}
WinShiftLoseStayAgent <- function(prevChoice, Feedback){
  if (Feedback == 1) {
    choice = 1 - prevChoice
  } else if (Feedback == 0) {
      choice = prevChoice
      }
  return(choice)
}
```

### Letting it play against the random agent with a bias of 0.7

```{r}
# Creating empty vectors for the players
Self <- rep(NA, trials)
Other <- rep(NA, trials)

# Defining random strategy for first trial of the wsls agent 
Self[1] <- RandomAgent(1, 0.5)

# Defining our random agent
rate <-  0.7
Other <- RandomAgent(seq(trials), rate)
  
# Defining the subsequent 
for (i in 2:trials) {
  
  # If the choice of self is the same as the choice of other then feedback is 1 (=win)
  if (Self[i - 1] == Other[i - 1]) {
    Feedback = 1
    # Otherwise feedback is 0 (=loss)
  } else {Feedback = 0}
  
  # The choice of self on a given trial is defined by the WinShiftLoseStay strategy (function) - the previous choice of self and the feedback 
  Self[i] <- WinShiftLoseStayAgent(Self[i - 1], Feedback)
}

```

### Creating tibble with the choices of self and other
```{r}
df_wsls_vs_random <- tibble(Self, Other, trial = seq(trials), Feedback = as.numeric(Self == Other))

```

### 
```{r}
df_wsls_vs_random$cumulativerateSelf <- 
  cumsum(df_wsls_vs_random$Feedback) / seq_along(df_wsls_vs_random$Feedback)
df_wsls_vs_random$cumulativerateOther <- 
  cumsum(1 - df_wsls_vs_random$Feedback) / seq_along(df_wsls_vs_random$Feedback)

wsls_vs_random <- ggplot(df_wsls_vs_random) + theme_classic() +
  geom_line(color = "plum4", aes(trial, cumulativerateSelf)) +
  geom_line(color = "skyblue3", aes(trial, cumulativerateOther))+
  ggtitle("WSLS agent vs random agent")

ggsave("plots/wsls_vs_random.png", width = 8, height = 6)
```


## Implementing imperfect memory agent 

"A player could not be able to keep in mind all previous trials, or decide to forget old trials, in case the biase shifts over time. So we could use only the last n trials, or do a weighted mean with weigths proportional to temporal closeness (the more recent, the higher the weight)."

- perfect memory the first Last_n_trials 
```{r}

ImperfectMemoryAgent <- function(Other, Last_n_trials){ 

  # given the Last_n_trials of the other give a certain choice 
  choice = round(mean(tail(Other, n = Last_n_trials)))
  
  return(choice)
}
```

### Making it play against the random agent
```{r}
# Creating empty vectors for the players 
Self <- rep(NA, trials)
Other <- rep(NA, trials)

# Defining random strategy for first trial of the imperfect memory agent 
Self[1] <- RandomAgent(1, 0.5)

# Defining our random agent
rate <-  0.7
Other <- RandomAgent(seq(trials), rate)

# Defining last n trials
Last_n_trials = 3

# Defining the subsequent 
for (i in 2:trials) {

  # window of memory
  # base the choice on the the tail of the memory until now
  history <- Other[1:i]
  
  if (length(history) < Last_n_trials) {
    Self[i] <- round(mean(history))
  } else {
    Self[i] <- ImperfectMemoryAgent(history, Last_n_trials)
  }
}

```

### Creating tibble with the choices of self and other
```{r}
df_IM_vs_random <- tibble(Self, Other, trial = seq(trials), Feedback = as.numeric(Self == Other))

```

### 
```{r}
df_IM_vs_random$cumulativerateSelf <- 
  cumsum(df_IM_vs_random$Feedback) / seq_along(df_IM_vs_random$Feedback)
df_IM_vs_random$cumulativerateOther <- 
  cumsum(1 - df_IM_vs_random$Feedback) / seq_along(df_IM_vs_random$Feedback)

ggplot(df_IM_vs_random) + theme_classic() +
  geom_line(color = "plum4", aes(trial, cumulativerateSelf)) +
  geom_line(color = "skyblue3", aes(trial, cumulativerateOther))+
  ggtitle("Imperfect memory agent vs random agent")

ggsave("plots/IM_vs_random.png", width = 8, height = 6)
```
